<!DOCTYPE HTML>
<!DOCTYPE html PUBLIC "" ""><HTML><HEAD>
<META http-equiv="Content-Type" content="text/html; charset=utf-8"></HEAD>
<BODY>
<PRE>---
title: "Week 9 R Assignment"
output: html_document
---




```{r}
library(RSQLite)
setwd('C:/Users/Game/Desktop/')
sqlite &lt;- dbDriver("SQLite")
workingdb &lt;- dbConnect(sqlite, "cunyweek9.sqlite")
dbListTables(workingdb)
I &lt;- dbSendQuery(workingdb, "SELECT * FROM I")
Idf &lt;- data.frame(fetch(I, -1))
II &lt;- dbSendQuery(workingdb, "SELECT * FROM II")
IIdf &lt;- data.frame(fetch(II, -1))
III &lt;- dbSendQuery(workingdb, "SELECT * FROM III")
IIIdf &lt;- data.frame(fetch(III, -1))
IV &lt;- dbSendQuery(workingdb, "SELECT * FROM IV")
IVdf &lt;- data.frame(fetch(IV, -1))
dbDisconnect(workingdb)
remove(sqlite)
remove(workingdb)
remove(I, II, III, IV)
par(mfrow=c(2,2))
plot(Idf, main="I")
abline(lm(Idf$y ~ Idf$x))
plot(IIdf, main="II")
abline(lm(IIdf$y ~ IIdf$x))
plot(IIIdf, main="III")
abline(lm(IIIdf$y ~ IIIdf$x))
plot(IVdf, main="IV")
abline(lm(IVdf$y ~ IVdf$x))
```


We can see that all four have a very similar regression line, but obviously those regression lines don't tell us very much about II, III, or IV


```{r}
summary(Idf)
```


```{r}
summary(IIdf)
```


```{r}
summary(IIIdf)
```


```{r}
summary(IVdf)
```
Summary statistics! Now we're getting somewhere.


Now let's create linear models and see how they look when graphed: \newpage
I:
```{r}
par(mfrow=c(2,2))
Ilm &lt;- lm(formula = y ~ x, data = Idf)
plot(Ilm)
```
\newpage
II:
```{r}
par(mfrow=c(2,2))
IIlm &lt;- lm(formula = y ~ x, data = IIdf)
plot(IIlm)
```
\newpage
III:
```{r}
par(mfrow=c(2,2))
IIIlm &lt;- lm(formula = y ~ x, data = IIIdf)
plot(IIIlm)
```
\newpage
IV:
```{r}
par(mfrow=c(2,2))
IVlm &lt;- lm(formula = y ~ x, data = IVdf)
plot(IVlm)
```


Now we have much better predictors for our data.


Influence Measures gives several measures of influence for each observation (Cook's Distance, et) and actually flags observations that it determines are influential by any of the measure

```{r}
influence.measures(Ilm)
```

```{r}
influence.measures(IIlm)
```

```{r}
influence.measures(IIIlm)
```

```{r}
influence.measures(IVlm)
```
</PRE></BODY></HTML>
